---
title: "Tableau Project 2"
output: html_document
---
Created by: Natasha Halfin, Evan Johnston, and Kaylyn Zvonek 

```{r, echo=TRUE}
library("ggplot2")
library("gplots")
library("bitops")
library("knitr")
library("jsonlite")
library("ggthemes")
library("RCurl")
library("reshape2")
library("tidyr")
library("dplyr")
library("grid")
```

```{r, eval = TRUE, echo=TRUE}
source("../01 SQL Crosstabs/sqlCrosstabs.R")

```


This rank crosstab partitions by Industry and ranks each Company within the Industry by Revenue.  
```{r, eval=TRUE, echo=TRUE}
head(dfRANKREVENUE)
```


This crosstab partitions companies by State, is sorted by Growth, then reports the max Growth for each State in a max_Growth column. Then another column is created with the difference between the company with the maximum growth and all other companies within the State. 
```{r, eval=TRUE, echo=TRUE}
head(dfMAX)
```
This crosstab partitions the companies by industry then returns the nth highest growth in each industry. In our case it returns the 2nd highest growth for each industry in a column called Second_Growth. 
```{r, eval=TRUE, echo=TRUE}
head(dfnth)
```
This crosstab first partitions the companies by state and orders them by revenue. Then it gives the cumulative distribution of the revenue of each company within the state partition.
```{r, eval=TRUE, echo=TRUE}
head(dfcume_dist)
```


