---
title: "DV_RProject2"
output: html_document
---

Natasha Halfin, Evan Johnston, Kaylyn Zvonek

For this project, we used a dataset containing information on the top 5000 companies in the country, including their state, city, industry, revenue, and percentage of growth.

```{r, echo=TRUE}
library("ggplot2")
library("gplots")
library("bitops")
library("knitr")
#library("plyr")
library("RCurl")
library("reshape2")
library("tidyr")
library("dplyr")
```

```{r, eval = TRUE, echo=TRUE}
source("../01 Data/data.R")
source("../02 Data Wrangling/dataWrangling.R")
```

This is a dataframe of our entire dataset.

```{r, eval =TRUE, echo=TRUE}
data.frame(head(companyData))
```
This is a dataframe of a subset of our data displaying companies in Texas that are in the IT services industry.
```{r, eval =TRUE, echo=TRUE}
data.frame(head(subset1))
```

This is a dataframe of wrangled data that indicates the average revenue and growth across each industry.

```{r, eval =TRUE, echo=TRUE}
data.frame(head(industryGrowthData))
```

This is a wrangled dataframe displaying companies in Texas and California and their industries.

```{r, eval =TRUE, echo=TRUE}
data.frame(head(txCaCompanyData))
```

This wrangled dataframe shows the highest revenue and growth by state.
```{r, eval =TRUE, echo=TRUE}
data.frame(head(stateGrowth))
```
This wrangled dataframe indicates the lowest revenue and growth by city.
```{r, eval =TRUE, echo=TRUE}
data.frame(head(cityGrowth))
```
**Data Visualizations**

```{r, eval = TRUE, echo=TRUE}
source("../03 Visualizations/viz1.R")
source("../03 Visualizations/viz2.R")
source("../03 Visualizations/viz3.R")
source("../03 Visualizations/viz4.R")
```
**Industry Revenues**

This plot shows the average revenue for each industry. Because the revenues are so varied, they are split up into 6 groups of similar revenue values.

```{r, echo=TRUE, warning=FALSE}
plot(viz1)
```

**Industry Growth**

This plot shows the average growth for each industry, ordered from least growth to most

```{r, echo=TRUE, warning=FALSE}
plot(viz2)
```

**Revenue and Growth by State**

This plot shows the highest revenues and highest growth rates of each state as a percent of the maximum.

```{r, echo=TRUE, warning=FALSE}
plot(viz3)
```

**State Growth**

This plot shows a comparison between number of companies in each industry for California and Texas

```{r, echo=TRUE, warning=FALSE}
plot(viz4)
```
